All the concepts behind TrueSkill Through Time: the \proglang{R}, \proglang{Python} and \proglang{Julia} packages (Draft)

### 2020-10-23 article.tex
Paper TTT: Detalles de cosas para hacer

\subsection{Example 2 old implementation}
As we can see, the implantation requires a more manual job, by defining dictionary and also adding noise to the priors, like the TrueSkill algorithm suggest. This default noise can be change to other. 
The only thing we must do manually its to pass the input in the correct format.
\lstinputlisting{./code/Example2.py}
[Out]:Time $7.7$ $10^{-3}$ seconds

In this example, we use the method get, so we can use the global prior only for the first game for each player.
As the same way of the first example, we are updating the prior of each player with the posterior of each game.
In this case we are saving this in a dictionary with the name of each player as key.
Printing at the end this, we will have each player with the latest posterior.

% explicar como usar la salida
\subsection{Example 2 new implementation}
\lstinputlisting{./code/Example2-1.py}
[Out]:Time $2.8$ $10^{-3}$ seconds

In this new implementation, we create a object of the method \texttt{history}, passing it the game composition, that is a list with a list for each game, and inside one list for each team, and also passing the result of each game.
REVISAR SI PASE BIEN EL RESULT.
Then using the method \texttt{trueskill} in this object, we compute the posteriors. 
ONLINE NO SERIA TRUE PARA SER CMOMO TRUESKILL?
For last, we can see the last posterior of each player, calling the method \texttt{posteriors\_players()}
Like we can see, the new way of implementation its more compact and simple than the original.

\subsection{Example 3: Trueskill True Time}
As it was mentioned already, one of the advantage of \textbf{TTT}, its the way that the algorithm pass information to the past to the future and vice versa, getting a more accurate estimation.
This package is the first implementation of this method, beside the original \texttt{Microsoft} package in \texttt{F\#}, of not free access. CHEQUEAR ESTO
For that, we use the next example. 
Three player, three games, that each one wins one game and lose the other one. 
So if we do TrueSkill, the order of how we compute the games will have importance, making at the end three player with three different skill. 
With \textbf{TTT} this kind of problem its solve.

@@

\begin{figure}[h!]
\centering
\includegraphics{jsslogo}
\caption{\label{fig:quine} Frequency distribution for number of days absent
from school.}
\end{figure}

>>>>

% \subsubsection{Existing Implementation}
% 
% As we can see, the implantation requires a more manual job, by defining dictionary and also adding noise to the priors, like the TrueSkill algorithm suggest. This default noise can be change to other. 
% The only thing we must do manually its to pass the input in the correct format.
% \lstinputlisting{./code/Example2.py}
% [Out]:Time $7.7$ $10^{-3}$ seconds
% 
% In this example, we use the method get, so we can use the global prior only for the first game for each player.
% As the same way of the first example, we are updating the prior of each player with the posterior of each game.
% In this case we are saving this in a dictionary with the name of each player as key.
% Printing at the end this, we will have each player with the latest posterior.
% 
% % explicar como usar la salida
% \subsubsection{Our proposed Implementation}
\lstinputlisting{./code/Example2-1.py}
[Out]:Time $2.8$ $10^{-3}$ seconds
\todo[inline]{No olvidar agregar los prints que muestra este c\'odigo, no solo el Out}

We create an instance of the class \texttt{history} and use it as parameter for the game composition.
This object contains the list of game's results.

\todo[inline]{Explicar qu'e es history bien y mostrar un ejemplo}
Then using the method \texttt{trueskill} in this object, we compute the posteriors. 
ONLINE NO SERIA TRUE PARA SER CMOMO TRUESKILL?
For last, we can see the last posterior of each player, calling the method \texttt{posteriors\_players()}
Like we can see, the new way of implementation its more compact and simple than the original.

\subsection{Example 3: Trueskill True Time}

As it was mentioned already, one of the advantage of \textbf{TTT}, its the way that the algorithm pass information to the past to the future and vice versa, getting a more accurate estimation.
This package is the first implementation of this method, beside the original \texttt{Microsoft} package in \texttt{F\#}, of not free access. CHEQUEAR ESTO
For that, we use the next example. 
Three player, three games, that each one wins one game and lose the other one. 
So if we do TrueSkill, the order of how we compute the games will have importance, making at the end three player with three different skill. 
With \textbf{TTT} this kind of problem its solve.

@@

\subsection{Example 4: Estimating the Evolution of the Skill}

\todo{inline]{poner el ejemplo de seguimiento de la habilidad de un jugador a medida que van pasando los partidos con una funci\'on de evoluci\'on conocida. ejemplo sinte\'etico}

\subsection{Example 5: Performance Analysis}

\todo[inline]{Aca tendremos dos figuras analizando la base de Go: 1) TT original, TT nuestro, TT-R y TT-Julia ; y otra figura con TTT: Python, Julia y R}
